Correlation of filter methods

### 2020-02-19 analysis/filter-correlation.Rmd

# load drake objects
drake::loadd(
  fv_nri_car, fv_nri_info.gain, fv_nri_gain.ratio,
  fv_nri_symuncert, fv_nri_relief,
  fv_nri_rank, fv_nri_cor,
  fv_nri_mrmr,
  fv_nri_cmim, fv_nri_var,

  fv_vi_car, fv_vi_info.gain, fv_vi_gain.ratio,
  fv_vi_symuncert, fv_vi_relief,
  fv_vi_rank, fv_vi_cor,
  fv_vi_mrmr,
  fv_vi_cmim, fv_vi_var,

  fv_hr_car, fv_hr_info.gain, fv_hr_gain.ratio,
  fv_hr_symuncert, fv_hr_relief,
  fv_hr_rank, fv_hr_cor,
  fv_hr_mrmr,
  fv_hr_cmim, fv_hr_var,

  fv_hr_info.gain5, fv_hr_info.gain10,
  fv_hr_info.gain15, fv_hr_info.gain20,
  fv_hr_info.gain25, fv_hr_info.gain30,

  fv_vi_info.gain5, fv_vi_info.gain10,
  fv_vi_info.gain15, fv_vi_info.gain20,
  fv_vi_info.gain25, fv_vi_info.gain30,

  fv_nri_info.gain5, fv_nri_info.gain10,
  fv_nri_info.gain15, fv_nri_info.gain20,
  fv_nri_info.gain25, fv_nri_info.gain30
)
```

@@

```{r filter-correlation-1, warning=FALSE}
# combine filter values

fv_all <- dplyr::bind_rows(
  fv_vi_car$data,
  fv_vi_info.gain$data,
  fv_vi_gain.ratio$data,
  fv_vi_symuncert$data,
  fv_vi_relief$data,
  fv_vi_rank$data,
  fv_vi_cor$data,
  fv_vi_mrmr$data,
  fv_vi_cmim$data,
  fv_vi_var$data
) %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:89, 10)) %>%
  tidyr::spread(filter, value) %>%
  mutate_if(is.numeric, list(~ na_if(., -Inf))) %>% # Inf in mrmr
  na.omit() %>% # NA in cmim
  dplyr::select(-id)

corr <- cor(fv_all, method = "spearman")
# p.mat = cor_pmat(corr)

ggcorrplot(corr,
  # p.mat = p.mat,
  hc.order = F,
  type = "lower",
  lab = TRUE
)
```

### Number of bins of `FSelectorRcpp::information.gain()`

```{r correlation-nbins, warning=FALSE, dev = c("png", "pdf")}
# recode levels so that they are unique
fv_all_list <- map2(
  list(
    fv_vi_info.gain5$data, fv_vi_info.gain10$data,
    fv_vi_info.gain15$data, fv_vi_info.gain20$data,
    fv_vi_info.gain25$data, fv_vi_info.gain30$data
  ),
  list(5, 10, 15, 20, 25, 30), ~
  dplyr::mutate(.x, filter = recode(.x$filter, FSelectorRcpp_information.gain = glue("FSelectorRcpp_information.gain-{.y}")))
)

fv_all <- dplyr::bind_rows(
  fv_all_list
) %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:89, 6)) %>%
  tidyr::spread(filter, value) %>%
  mutate_if(is.numeric, list(~ na_if(., -Inf))) %>% # Inf in mrmr
  na.omit() %>%
  dplyr::select(-id)

corr <- cor(fv_all, method = "spearman")

ggcorrplot(corr,
  # p.mat = p.mat,
  hc.order = F,
  type = "lower",
  lab = TRUE
)
```

@@

```{r correlation-filter-nri, dev = c("png", "pdf"), warning=FALSE}
# combine filter values

fv_all <- dplyr::bind_rows(
  fv_nri_car$data,
  fv_nri_info.gain$data,
  fv_nri_gain.ratio$data,
  fv_nri_symuncert$data,
  fv_nri_relief$data,
  fv_nri_rank$data,
  fv_nri_cor$data,
  fv_nri_mrmr$data,
  fv_nri_cmim$data,
  fv_nri_var$data
) %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:7381, 10)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

corr <- cor(fv_all, method = "spearman")
p.mat <- cor_pmat(corr)

ggcorrplot(corr,
  # p.mat = p.mat,
  hc.order = FALSE,
  type = "lower",
  lab = TRUE
)
```

@@

```{r filter-correlation-4, warning=FALSE}
# combine filter values

fv_all <- dplyr::bind_rows(
  fv_hr_car$data,
  fv_hr_info.gain$data,
  fv_hr_gain.ratio$data,
  fv_hr_symuncert$data,
  fv_hr_relief$data,
  fv_hr_rank$data,
  fv_hr_cor$data,
  fv_hr_mrmr$data,
  fv_hr_cmim$data,
  fv_hr_var$data
) %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:122, 10)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

corr <- cor(fv_all, method = "spearman")
p.mat <- cor_pmat(corr)

ggcorrplot(corr,
  # p.mat = p.mat,
  hc.order = F,
  type = "lower",
  lab = TRUE
)
```

>>>>

# load drake objects
drake::loadd(
  filter_values,
  filter_values_fselectorrcpp,

  filter_info_gain_nbins
)
```

@@

The idea behind is was to analyze the correlation between filter rankings.
We only wanted to included filters which have a somewhat unique ranking.
Otherwise, when creating ensemble filters, certain filters would implicitly be weighted more than others.

Takeaway:

- Only use one of "information gain", "gain ratio", "sym uncert"

- Either use Spearman or Pearson correlation

```{r filter-correlation-1, warning=FALSE}
fv_all_vi <- map(filter_values[8:14], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:89, 7)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

fv_all_vi_fselecrcpp <- map(filter_values_fselectorrcpp[4:6], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:89, 3)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

fv_all_vi_merged <- bind_cols(fv_all_vi, fv_all_vi_fselecrcpp)

corr_vi <- cor(fv_all_vi_merged, method = "spearman")

ggcorrplot(corr_vi,
  # p.mat = p.mat,
  hc.order = F,
  type = "lower",
  lab = TRUE
)
```

@@

```{r correlation-filter-nri, dev = c("png", "pdf"), warning=FALSE}
fv_all_nri <- map(filter_values[15:21], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:7381, 7)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

fv_all_nri_fselecrcpp <- map(filter_values_fselectorrcpp[7:9], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:7381, 3)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

fv_all_nri_merged <- bind_cols(fv_all_nri, fv_all_nri_fselecrcpp)

corr_nri <- cor(fv_all_nri_merged, method = "spearman")

ggcorrplot(corr_nri,
  # p.mat = p.mat,
  hc.order = F,
  type = "lower",
  lab = TRUE
)
```

@@

```{r filter-correlation-4, warning=FALSE}
fv_all_hr <- map(filter_values[1:7], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:122, 7)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

fv_all_hr_fselecrcpp <- map(filter_values_fselectorrcpp[1:3], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(1:122, 3)) %>%
  tidyr::spread(filter, value) %>%
  dplyr::select(-id)

fv_all_hr_merged <- bind_cols(fv_all_hr, fv_all_hr_fselecrcpp)

corr_hr <- cor(fv_all_hr_merged, method = "spearman")

ggcorrplot(corr_hr,
  # p.mat = p.mat,
  hc.order = F,
  type = "lower",
  lab = TRUE
)
```

## Number of bins of `FSelectorRcpp::information.gain()`

Analyzing the effect of a different `nbins` value on the filter values of filter "Information Gain".

- Lower correlation / highest difference: `nbins = 5` vs. `nbins = 30`

-> We decided to use with `nbins = 10` in the analysis.

The hidden default of nbins when setting `equal = TRUE` in `FSelectorRcpp::information_gain()` is 5.

```{r correlation-nbins, warning=FALSE, dev = c("png", "pdf")}
# recode levels so that they are unique
fv_info_gain <- map(filter_info_gain_nbins[1:6], ~ .x[["data"]]) %>%
  dplyr::bind_rows() %>%
  dplyr::select(value, filter) %>%
  mutate(id = rep(seq(5, 30, 5), each = 122)) %>%
  tidyr::unite(filter, c("filter", "id")) %>%
  mutate(id = rep(seq(1, length(.data$value) / 6), 6)) %>%
  tidyr::pivot_wider(
    names_from = filter,
    values_from = value
  ) %>%
  dplyr::select(-id)

corr_inf_gain <- cor(fv_info_gain, method = "spearman")

ggcorrplot(corr_inf_gain,
  # p.mat = p.mat,
  hc.order = F,
  type = "lower",
  lab = TRUE
)
```
